Results

### 2018-06-25 02_analysis.Rmd
Cooler color system

```{r fig-ngo-favorability, fig.width=7, fig.height=4}
ngo_favorability_raw <- results %>%
  select(favor_humanitarian, favor_human_rights, favor_development) %>% 
  gather(variable, value) %>% 
  count(variable, value) %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  left_join(favorability_cols_5, by = "value") %>% 
  mutate(clean_name = str_replace(clean_name, "towards", "towards\n")) %>% 
  mutate(value = factor(value, levels = levels(results$favor_humanitarian), ordered = TRUE),
         clean_name = fct_inorder(clean_name, ordered = TRUE)) %>%
  arrange(value) %>% 
  mutate(color = fct_inorder(color, ordered = TRUE))

@@

plot_donate_summary <- ggplot(donate_summary, aes(x = n, y = donate_likely, 
                                                  fill = highlight)) +
  geom_barh(stat = "identity") +
  scale_x_continuous(sec.axis = sec_axis(~ . / sum(donate_summary$n),
                                         labels = percent)) +
  scale_fill_manual(values = c(ngo_green, ngo_blue), guide = FALSE) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

```{r fig-amount-bars, fig.width=9, fig.height=2.75}
plot_amount_summary <- ggplot(results, aes(x = amount_donate)) +
  geom_histogram(bins = 20, fill = ngo_blue) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

@@

plot_amount_c <- ggplot(coef_summary_c, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

@@

plot_amount_ci <- ggplot(coef_summary_ci, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_blue) + 
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue)
```

@@

plot_amount_cif <- ggplot(coef_summary_cif, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_red) +
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue + funding)
```

@@

plot_amount_singles <- ggplot(coef_summary_singles, aes(y = estimate, x = value)) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = condition)) +
  scale_y_continuous(labels = dollar) +
  scale_color_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
  labs(x = NULL, y = "Median amount donated") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ condition, scales = "free_x")

@@

plot_diffs_c <- ggplot() + 
  geom_density(data = pairs_plot_data_c, aes(x = value),
               fill = ngo_green, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_pairs_detail_c, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_c, aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)
```

@@

plot_diffs_ci <- ggplot() + 
  geom_density(data = pairs_plot_data_ci, aes(x = value),
               fill = ngo_blue, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_pairs_detail_ci, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_ci, aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + pair)
```

@@

plot_diffs_cif <- ggplot() + 
  geom_density(data = pairs_plot_data_cif, aes(x = value),
               fill = ngo_red, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_pairs_detail_cif, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_cif, aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + funding + pair)
```

@@

plot_diffs_singles <- ggplot() +
  geom_density(data = diffs_plot_data_singles, 
               aes(x = value, fill = pair),
               colour = NA, alpha = 0.4) +
  geom_segment(data = diffs_coef_pairs_detail_singles, 
               aes(x = q5, xend = q95, y = 0, yend = 0, group = pair),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_singles, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_x_continuous(labels = dollar) +
  scale_fill_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)

@@

plot_likely_c <- ggplot(coef_summary_likely_c, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

@@

plot_likely_i <- ggplot(coef_summary_likely_i, aes(y = estimate, x = issue)) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

@@

plot_likely_f <- ggplot(coef_summary_likely_f, aes(y = estimate, x = funding)) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

@@

plot_likely_ci <- ggplot(coef_summary_likely_ci, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_blue) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue)
```

@@

plot_likely_cif <- ggplot(coef_summary_likely_cif, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_red) +
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue + funding)
```

@@

plot_diffs_likely_c <- ggplot() + 
  geom_density(data = pairs_likely_plot_data_c, aes(x = value),
               fill = ngo_green, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_likely_pairs_detail_c, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_c, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)
```

@@

plot_diffs_likely_ci <- ggplot() + 
  geom_density(data = pairs_likely_plot_data_ci, aes(x = value),
               fill = ngo_blue, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_likely_pairs_detail_ci, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_ci, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + pair)
```

@@

plot_diffs_likely_cif <- ggplot() + 
  geom_density(data = pairs_likely_plot_data_cif, aes(x = value),
               fill = ngo_red, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_likely_pairs_detail_cif, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_cif, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + funding + pair)
```

@@

plot_diffs_likely_singles <- ggplot() +
  geom_density(data = diffs_likely_plot_data_singles, 
               aes(x = value, fill = pair),
               colour = NA, alpha = 0.4) +
  geom_segment(data = diffs_coef_likely_pairs_detail_singles, 
               aes(x = q5, xend = q95, y = 0, yend = 0, group = pair),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_singles, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_x_continuous(labels = percent) +
  scale_fill_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)

>>>>

```{r fig-ngo-favorability, fig.width=7, fig.height=4}
favorability_cols <- data_frame(value = c("Very unfavorable", "Unfavorable", "Neutral",
                                          "Favorable", "Very favorable"),
                                color = ngo_pal("ordered")(5))

ngo_favorability_raw <- results %>%
  select(favor_humanitarian, favor_human_rights, favor_development) %>% 
  gather(variable, value) %>% 
  count(variable, value) %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  left_join(favorability_cols, by = "value") %>%
  mutate(clean_name = str_replace(clean_name, "towards", "towards\n")) %>% 
  mutate(value = factor(value, levels = levels(results$favor_humanitarian), ordered = TRUE),
         clean_name = fct_inorder(clean_name, ordered = TRUE)) %>%
  arrange(value) %>% 
  mutate(color = fct_inorder(color, ordered = TRUE))

@@

plot_donate_summary <- ggplot(donate_summary, aes(x = n, y = donate_likely, 
                                                  fill = highlight)) +
  geom_barh(stat = "identity") +
  scale_x_continuous(sec.axis = sec_axis(~ . / sum(donate_summary$n),
                                         labels = percent)) +
  scale_fill_manual(values = ngo_cols("green", "blue", name = FALSE), guide = FALSE) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

plot_donate_summary

@@

```{r fig-amount-bars, fig.width=9, fig.height=2.75}
plot_amount_summary <- ggplot(results, aes(x = amount_donate)) +
  geom_histogram(bins = 20, fill = ngo_cols("blue")) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

@@

plot_amount_c <- ggplot(coef_summary_c, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

@@

plot_amount_ci <- ggplot(coef_summary_ci, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("blue")) + 
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue)
```

@@

plot_amount_cif <- ggplot(coef_summary_cif, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("red")) +
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue + funding)
```

@@

plot_amount_singles <- ggplot(coef_summary_singles, aes(y = estimate, x = value)) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = condition)) +
  scale_y_continuous(labels = dollar) +
  scale_color_manual(values = ngo_cols("green", "blue", "red", name = FALSE), guide = FALSE) +
  labs(x = NULL, y = "Median amount donated") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ condition, scales = "free_x")

@@

plot_diffs_c <- ggplot() + 
  geom_density(data = pairs_plot_data_c, aes(x = value),
               fill = ngo_cols("green"), colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_pairs_detail_c, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_c, aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)
```

@@

plot_diffs_ci <- ggplot() + 
  geom_density(data = pairs_plot_data_ci, aes(x = value),
               fill = ngo_cols("blue"), colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_pairs_detail_ci, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_ci, aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + pair)
```

@@

plot_diffs_cif <- ggplot() + 
  geom_density(data = pairs_plot_data_cif, aes(x = value),
               fill = ngo_cols("red"), colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_pairs_detail_cif, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_cif, aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + funding + pair)
```

@@

plot_diffs_singles <- ggplot() +
  geom_density(data = diffs_plot_data_singles, 
               aes(x = value, fill = pair),
               colour = NA, alpha = 0.4) +
  geom_segment(data = diffs_coef_pairs_detail_singles, 
               aes(x = q5, xend = q95, y = 0, yend = 0, group = pair),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_singles, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_x_continuous(labels = dollar) +
  scale_fill_manual(values = ngo_cols("green", "blue", "red", name = FALSE), guide = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)

@@

plot_likely_c <- ggplot(coef_summary_likely_c, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

@@

plot_likely_i <- ggplot(coef_summary_likely_i, aes(y = estimate, x = issue)) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

@@

plot_likely_f <- ggplot(coef_summary_likely_f, aes(y = estimate, x = funding)) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

@@

plot_likely_ci <- ggplot(coef_summary_likely_ci, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("blue")) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue)
```

@@

plot_likely_cif <- ggplot(coef_summary_likely_cif, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("red")) +
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue + funding)
```

@@

plot_diffs_likely_c <- ggplot() + 
  geom_density(data = pairs_likely_plot_data_c, aes(x = value),
               fill = ngo_cols("green"), colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_likely_pairs_detail_c, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_c, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)
```

@@

plot_diffs_likely_ci <- ggplot() + 
  geom_density(data = pairs_likely_plot_data_ci, aes(x = value),
               fill = ngo_cols("blue"), colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_likely_pairs_detail_ci, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_ci, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + pair)
```

@@

plot_diffs_likely_cif <- ggplot() + 
  geom_density(data = pairs_likely_plot_data_cif, aes(x = value),
               fill = ngo_cols("red"), colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_likely_pairs_detail_cif, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_cif, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + funding + pair)
```

@@

plot_diffs_likely_singles <- ggplot() +
  geom_density(data = diffs_likely_plot_data_singles, 
               aes(x = value, fill = pair),
               colour = NA, alpha = 0.4) +
  geom_segment(data = diffs_coef_likely_pairs_detail_singles, 
               aes(x = q5, xend = q95, y = 0, yend = 0, group = pair),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_singles, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_x_continuous(labels = percent) +
  scale_fill_manual(values = ngo_cols("green", "blue", "red", name = FALSE), guide = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)
